\cventry{2016}
    {Hazur}
    {}
    {\scriptsize Ruby On Rails, MySQL, SASS}
    {}
    {
       A Personal Psychiatrist which helps in solving problem using Shri Guru Granth Sahib Ji. 
        \hfill
        \href{http://github.com/amitojsingh/Hazur}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}

\cventry{2015}
    {Lord Byron}
    {}
    {\scriptsize meteor, Javascript}
    {}
    {
        Lord Byron is a real time editor built using Meteor.
        In this all users can edit the same document at same time, and also observe the changes of other users in real time.
        Apart from being real time the main feature of this editor is to check grammar. It uses Natural Language Processing (NLP) to check the grammar. It highlights various parts of speech.
    }
    \vspace*{0.2\baselineskip}

\cventry{2014}
    {ABCD Fonts}
    {}
    {\scriptsize PHP, HTML, CSS}
    {}
    {
        ABCD Fonts is collection of different types of Punjabi font which we can use in our website as well as can download and used in posters.
        \hfill
        \href{https://github.com/amitojsingh/ABCD-fonts}{\textcolor{blue}{\scriptsize Code.}}
    }
    \vspace*{0.2\baselineskip}
    
\cventry{2013}
    {Laka Blogging Engine}
    {}
    {\scriptsize Webtoolkit(Wt), C++, Bootstrap}
    {}
    {Laka Blogging Engine is blogging Engine which is developed purely in C++}

\cventry{2012}
{Web Through C}
{}
{\scriptsize C, CSS, HTML}
{}
{Web Through C is a small program which develop your website within a few minutes by simply entering the text and no codding skills are required for the user }